doe-pkgs-analysis

### 2021-09-12 analysis/doe-pkgs-analysis.Rmd
Create Sankey diagram for package type and domain.

```{r}
sankey_data <- pkg_tidy_long_type %>%
  select(year, domain, type) %>%
  group_by(domain, type) %>%
  count() %>%
  ungroup()
```

>>>>

```{r}
sankey_data <- pkg_tidy_long_type %>%
  select(year, domain, type) %>%
  group_by(domain, type) %>%
  count() %>%
  ungroup()

domain <- sankey_data %>%
  distinct(domain) %>%
  rename(node = domain)

type <- sankey_data %>%
  distinct(node = type)

db_sankey <- rbind(domain, type)

routes_sankey <- graph_from_data_frame(d = sankey_data, vertices = db_sankey, directed = TRUE)

routes_sankey_tidy <- routes_sankey %>% as_tbl_graph() %>%
  activate(edges)

nodes_sankey <- db_sankey %>%
  rowid_to_column("id") %>%
  mutate(id = id - 1)

edges_sankey <-routes_sankey_tidy %>%
  activate(edges) %>%
  data.frame() %>%
  mutate(from = from - 1,
         to = to - 1)

sankeyNetwork(Links = edges_sankey, Nodes = nodes_sankey, Source = 'from', 
                         Target = 'to', Value = 'n', NodeID = 'node',
                         units = 'packages')
```
